Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis

### 2019-09-09 AppendixS1.tex
Fix other appendix formatting/label issues

% Created 2019-09-09 Mon 09:26
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[backend=biber,style=authoryear,date=year]{biblatex}
\addbibresource{/Users/shik544/Dropbox/references/library.bib}
\input{authors.tex}
\date{}
\title{Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis}
\hypersetup{
 pdfauthor={},
 pdftitle={Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

\maketitle
\noindent \textbf{Journal:} Ecological Applications

\clearpage

>>>>

% Created 2019-09-09 Mon 09:38
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[backend=biber,style=authoryear,date=year]{biblatex}
\addbibresource{/Users/shik544/Dropbox/references/library.bib}
\date{}
\title{}
\hypersetup{
 pdfauthor={},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

\noindent \textbf{Title:}
Does the leaf economic spectrum hold within plant functional types?
A Bayesian multivariate trait meta-analysis

\noindent \textbf{Authors:}
Alexey N. Shiklomanov,
Elizabeth M. Cowdery,
Michael Bahn,
Chaeho Byun,
Steven Jansen,
Koen Kramer,
Vanessa Minden,
Ülo Niinemets,
Yusuke Onoda,
Nadejda A. Soudzilovskaia,
Michael C. Dietze

\noindent \textbf{Journal:} Ecological Applications

### 2019-09-09 AppendixS2.Rmd
Fix other appendix formatting/label issues

---
title: Supporting information
author:
  - >
    Alexey N. Shiklomanov,
    Elizabeth M. Cowdery,
    Michael Bahn,
    Chaeho Byun,
    Steven Jansen,
    Koen Kramer,
    Vanessa Minden,
    Ülo Niinemets,
    Yusuke Onoda,
    Nadejda A. Soudzilovskaia,
    Michael C. Dietze
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \renewcommand{\thetable}{S\arabic{table}}
  - \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

(Page intentionally left blank)

@@

# Method S1: Estimating trait means and covariances through multiple imputation {-}

@@

# Method S2: Biased mean estimates in non-representatively sampled bivariate data

>>>>

---
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \renewcommand{\thetable}{S\arabic{table}}
  - \renewcommand{\thefigure}{S\arabic{figure}}
---

**Title:** 
Does the leaf economic spectrum hold within plant functional types?
A Bayesian multivariate trait meta-analysis

**Authors:** 
Alexey N. Shiklomanov,
Elizabeth M. Cowdery,
Michael Bahn,
Chaeho Byun,
Steven Jansen,
Koen Kramer,
Vanessa Minden,
Ülo Niinemets,
Yusuke Onoda,
Nadejda A. Soudzilovskaia,
Michael C. Dietze

**Journal:** Ecological Applications

**Appendix S2: Supporting information**

@@

@@

# Section S1: Estimating trait means and covariances through multiple imputation {-}

@@

# Section S2: Biased mean estimates in non-representatively sampled bivariate data
